Analysing Constraint Grammars with a SAT-solver

### 2016-02-28 paper/lrec/eval_futurework.tex
add more tables; add text about finnish

\hline
              & \textsc{nld}  & \textsc{spa}  & \textsc{fin}  \\ \hline
\# rules      & 59              & 279      & 1185     \\ \hline
\# readings   & 336             & 2191     & 2012    \\ \hline
\# conflicts  & 7 (1 + 5 + 1)   & 1        & 51    \\ \hline
\clock{} all rules       & ??s              & ??min ??s    & ?h ??min    \\ \hline
\clock{} last rule       & ??s              & ??s          & ?min ??s    \\ \hline

@@

@@

\paragraph{Finnish} \todo{Rerun the tests and rewrite this whole section!} For the Finnish grammar, we did not have time to investigate all the
results. We could verify approximately \nicefrac{1}{3} as true positives and
\nicefrac{1}{3} as false positives.
The verified true positives were all rule-internal conflicts. 
For example, the following rule requires the target to be genitive and unambiguously nominative: 
\begin{itemize}
\item[]\texttt{"oma" SELECT GEN IF [...] (0C NOM) ;}
\end{itemize}
We also detected a number of tagset errors;
the grammar was originally written in 1995, and converted to the
Omorfi tagset by \cite{pirinen2015}, but there were 15 rules that used the old convention for possessive suffixes.

>>>>

\hline
                   & \textsc{nld}  & \textsc{spa}lem  & \textsc{spa}nolem \\ \hline
\# rules           & 59            & 279       & 279     \\ \hline
\# readings        & 336           & 3905      & 1735    \\ \hline
\# conflicts       & 7             & n         & m    \\ \hline
\clock{} all rules & ??s           & + 1h      & 30m-1h   \\ \hline
\clock{} last rule & ??s           & ??s       & ?min ??s    \\ \hline
\clock{} all rules 
without ambiguity 
classes            & 10ish sec       & ??min ??s    & ?h ??min    \\ \hline

@@

\hline
              & n clitics & m clitics & only underspecified \\ \hline
\# rules      & 1185      & 1185      & 1185\\ \hline
\# readings   & many & more & only like <2000   \\ \hline
\# conflicts  & n   & m        & super many    \\ \hline
\clock{} all rules       & ??s              & ??min ??s    & ?h ??min    \\ \hline
\clock{} last rule       & ??s              & ??s          & ?min ??s    \\ \hline

\end{tabular}
\caption{Special table for Finnish}
\label{table:resFin}
\end{table}

@@

\paragraph{Finnish} 
\todo{Rerun the tests and rewrite this whole section!}

The results for the Finnish grammar are shown separately, in table~\ref{table:resFin}.
We were not able to use the method with ambiguity classes at all---expanding the Finnish morphological lexicon results in \todo{100s of gigabytes?} of word forms, which is simply too big for our method to work. 
For future development, we will see if it is possible to manipulate the finite automata directly, instead of relying on the output in text.

In addition to the previous problem, we had a large number of readings. In order to make the test run faster, we tried a few shortcuts. First, we restricted the amount of clitics per word form, and even ignored all the specified readings

For the Finnish grammar, we did not have time to investigate all the
results. We could verify approximately \nicefrac{1}{3} as true positives and
\nicefrac{1}{3} as false positives.
The verified true positives were all rule-internal conflicts. 
For example, the following rule requires the target to be genitive and unambiguously nominative: 
\begin{itemize}
\item[]\texttt{"oma" SELECT GEN IF [...] (0C NOM) ;}
\end{itemize}
We also detected a number of tagset errors;
the grammar was originally written in 1995, and converted to the
Omorfi tagset by \cite{pirinen2015}, but there were 15 rules that used the old convention for possessive suffixes.
